Parsing Postfix log files

### 2008-08-07 doc/logparser-results.tex
Changed normal to optimal.

XXX CHANGE normal TO optimal IN ORDERING STUFF, INCLUDING IN GRAPH CAPTIONS
AND AXIS LABELS\@.

@@

    \item [normal]  The most optimal order, according to the hypothesis:
        rules which match most often will be tried first.

@@

\Graphref{Parsing time relative to shuffled ordering graph} shows the
parsing times of normal and reverse orderings relative to shuffled
ordering; the mean relative parsing times for different groupings of log
files are given in \tableref{Parsing time relative to shuffled ordering
table}.  Overall this optimisation provides a modest but worthwhile
performance increase of approximately 10\%, for a small investment in time
and programming.

\showgraph{build/graph-normal-and-reverse-vs-shuffle}{Parsing time relative
to shuffled ordering}{Parsing time relative to shuffled ordering graph}

\showtable{build/include-normal-and-reverse-vs-shuffle}{Parsing time
relative to shuffled ordering}{Parsing time relative to shuffled ordering
table}

@@

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this document is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of statistics was generated using
the minimum ruleset and compared to the statistics generated using the full
ruleset: the percentage parsing time increase when using the full ruleset
instead of the minimal ruleset for normal, shuffled and reversed orderings
is shown in \graphref{Percentage parsing time increase of maximum ruleset
over minimum ruleset}.

@@

It is clear from \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset} that the increased number of rules noticeably
increases parsing time with reverse ordering, and to a lesser extent with
shuffled ordering.  The normal ordering (where are the most frequently
matching rules are tried first) shows a mean increase of
\input{build/include-full-ruleset-vs-minimum-ruleset} in parsing time for a
\numberOFrulesMAXIMUMpercentage{} increase in the number of rules.  Log
files 22 and 62--68 show much smaller increases for shuffled and reversed
ordering than other log files do, because the majority of log lines in
those log files are parsed by Postfix components with a small number of
parsing rules, so removing unnecessary rules has little effect on the total
number of rules used.  These results show that the architecture scales very
well as the number of rules increases, and that optimally sorting the rules
is an important optimisation contributing to this scalability.

>>>>

@@

    \item [optimal]  The most optimal order, according to the hypothesis:
        rules which match most often will be tried first.

@@

\Graphref{Parsing time relative to shuffled ordering graph} shows the
parsing times of optimal and reverse orderings relative to shuffled
ordering; the mean relative parsing times for different groupings of log
files are given in \tableref{Parsing time relative to shuffled ordering
table}.  Overall this optimisation provides a modest but worthwhile
performance increase of approximately 10\%, for a small investment in time
and programming.

\showgraph{build/graph-optimal-and-reverse-vs-shuffle}{Parsing time relative
to shuffled ordering}{Parsing time relative to shuffled ordering graph}

\showtable{build/include-optimal-and-reverse-vs-shuffle}{Parsing time
relative to shuffled ordering}{Parsing time relative to shuffled ordering
table}

@@

How any architecture scales as the number of rules increases is important,
but it is particularly important in this architecture because it is
expected that the typical parser will have a large number of rules.  There
are \numberOFrules{} rules in the full Postfix ruleset, whereas the minimum
number of rules required to parse the \numberOFlogFILES{} log files used
when generating the results in this document is \numberOFrulesMINIMUM{},
\numberOFrulesMINIMUMpercentage{} of the full ruleset.  The full ruleset is
larger because the Postfix parser is tested with \numberOFlogFILESall{} log
files, to improve its parsing and ensure it correctly parses logs generated
by later Postfix versions.  A second set of statistics was generated using
the minimum ruleset and compared to the statistics generated using the full
ruleset: the percentage parsing time increase when using the full ruleset
instead of the minimal ruleset for optimal, shuffled and reversed orderings
is shown in \graphref{Percentage parsing time increase of maximum ruleset
over minimum ruleset}.

@@

It is clear from \graphref{Percentage parsing time increase of maximum
ruleset over minimum ruleset} that the increased number of rules noticeably
increases parsing time with reverse ordering, and to a lesser extent with
shuffled ordering.  The optimal ordering (where the most frequently
matching rules are tried first) shows a mean increase of
\input{build/include-full-ruleset-vs-minimum-ruleset} in parsing time for a
\numberOFrulesMAXIMUMpercentage{} increase in the number of rules.  Log
files 22 and 62--68 show much smaller increases for shuffled and reversed
ordering than other log files do, because the majority of log lines in
those log files are parsed by Postfix components with a small number of
parsing rules, so removing unnecessary rules has little effect on the total
number of rules used.  These results show that the architecture scales very
well as the number of rules increases, and that optimally sorting the rules
is an important optimisation contributing to this scalability.
